R for Clinical Study Reports and Submission

### 2023-07-09 preface.qmd
Break lines to 80 characters each and style code chunks

- Part 1, titled "Delivering TLFs in CSR," provides general information and examples on creating tables, listings, and figures. It assumes that readers are individual contributors to a clinical project with prior experience in R programming. Familiarity with data manipulation in R is expected. Some recommended references for this part include [Hands-On Programming with R](https://rstudio-education.github.io/hopr/),
  [R for Data Science](https://r4ds.had.co.nz/) and
  [Data Manipulation with R](https://www.amazon.com/Data-Manipulation-R-Use/dp/0387747303).

- Part 2, titled "Clinical trial project," provides general information and examples on managing a clinical trial A&R project. It assumes that readers are project leads who have experience in R package development. Recommended references for this part include [R Packages](https://r-pkgs.org/) and the
  [tidyverse style guide](https://style.tidyverse.org/).

- Part 3, titled "eCTD submission package," provides general information on preparing submission packages related to the CSR in the electronic Common Technical Document (eCTD) format. It assumes that readers are project leads of clinical projects who possess experience in R package development and submission.

@@

We share the same philosophy described in
the introduction of the [R Packages](https://r-pkgs.org/Introduction.html#intro-phil) book [@wickham2023r]
, which we quote below:

>>>>

- Part 1, titled "Delivering TLFs in CSR", provides general information and
  examples on creating tables, listings, and figures. It assumes that readers
  are individual contributors to a clinical project with prior experience in
  R programming. Familiarity with data manipulation in R is expected.
  Some recommended references for this part include
  [Hands-On Programming with R](https://rstudio-education.github.io/hopr/),
  [R for Data Science](https://r4ds.had.co.nz/), and
  [Data Manipulation with R](https://doi.org/10.1007/978-0-387-74731-6).

- Part 2, titled "Clinical trial project", provides general information and
  examples on managing a clinical trial A&R project. It assumes that readers
  are project leads who have experience in R package development.
  Recommended references for this part include
  [R Packages](https://r-pkgs.org/) and the
  [tidyverse style guide](https://style.tidyverse.org/).

- Part 3, titled "eCTD submission package", provides general information on
  preparing submission packages related to the CSR in the
  electronic Common Technical Document (eCTD) format.
  It assumes that readers are project leads of clinical projects who possess
  experience in R package development and submission.

@@

We share the same philosophy described in the introduction of the
[R Packages](https://r-pkgs.org/introduction.html#sec-intro-phil)
book [@wickham2023r], which we quote below:
